Universals of word order result from optimization of grammars for efficient communication

### 2019-03-22 second-draft/3-paper-names.tex
revising

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/communication.png}
	\caption{Our model of communication: A speaker (left) expresses a dependency structure into a string of words forming a sentence. A listener probabilistically recovers a dependency structure. In this example, the grammar of English allows the listener to recover the correct dependency structure with very high confidence.}
	\label{fig:comm}
\end{figure}

@@

%\subsection{Counterfactual Grammars}
We model the process where a speaker communicates a message to a listener (Figure~\ref{fig:comm}) in Shannon's framework of information theory.
In this model, a transmitter encodes a message into a signal. The receiver decodes the signal, attempting to reconstruct the original message.
Applying this model to word order, we take the message to consist of entities, events, and a set of syntactic and semantic relations that hold between them.
Following a long tradition in formal and computational liguistics, we formalize these in the format of Dependency Grammar:
This linguistic formalism draws directed arcs between syntactically related words, annotated with syntactic relations.
In Figure~\ref{fig:comm}, the message consists of a dependency structure with the words `saw', `Mary', `John', where Mary is the subject of the event denoted by `saw', and John is the object.

When uttering, the speaker needs to choose an ordering in which to order the words in this tree to generate a string of words.
Imagine the speaker wants to communicate that Mary saw John.
Should the speaker say (1) as in English, or (2) as in Japanese?

@@

The listener receives a sentence -- a linear string of words -- and decodes the underlying message.
Consistent with Shannon's model, we assume a Bayesian listener who decodes dependency structures probabilistically~(Figure~\ref{fig:comm}).
If communication is successful, the listener can identify the intended structure with high confidence~(Figure~\ref{fig:comm}).

@@

All natural languages have some degree of word order regularities that are specified in their grammar.
For instance, English places subjects before and objects after the verb, allowing the listener to unambiguously decode the sentence in Figure~\ref{fig:comm}.
That is, speakers and listeners have shared knowledge of a \key{grammar} that specifies how dependency structures are encoded into sentences.
Natural languages differ in the rules they apply: Some place the object after the verb, some place it before the verb.
%Speakers encode dependency trees into sentences according to a grammar~(Figure~\ref{fig:grammars}).
%While natural languages differ in the freedom of word order, all languages rely on some amount of word order reglarity to encode meaning.
This is illustrated in Figure~\ref{fig:grammars}: Grammars specify how dependency structures are encoded into strings of words.
For instance, Grammar 1 -- corresponding to Arabic in Figure~\ref{fig:arabic-japanese-simple} -- orders objects (`friends', `letter') after verbs and has prepositions (`to friend').
Grammar 2 orders objects after verbs but has postpositions (`friend -- to').
Grammars 3 and 4 place the object before the verb, and one of them (Grammar 3) corresponds to Japanese order.
We formalize word order grammars as specifying how different types of dependents (subjects, objects, etc.) are ordered, employing a cross-linguistically meaningful inventory of relations~\cite{nivre2015universal}.

%\subsection{Efficiency in Word Order}
Zipf

In Information Theory, the usefulness of a communication channel depends on (1) how costly encoding and transmission is, and (2) how precisely messages can be recovered from codes.

@@

>>>>

TODO maybe Arabic becomes English?

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/communication-two-langs.png}
	\caption{Grammars define communication channels: A speaker (left) expresses a dependency structure into a string of words forming a sentence. The order of words is determined by the grammar of the language. A listener recovers a dependency structure.}
	\label{fig:comm}
\end{figure}

@@

%\subsection{Counterfactual Grammars}
We model the process where a speaker communicates a message to a listener (Figure~\ref{fig:comm}) in Shannon's framework of information theory.
In this model, a transmitter encodes a message into a signal. The receiver decodes the signal, attempting to reconstruct the original message.
Applying this model to word order, we take the message to consist of entities, events, and a set of syntactic and semantic relations that hold between them.
Following a long tradition in formal and computational liguistics, we formalize these in the format of Dependency Grammar (CITE):
This linguistic formalism draws directed arcs between syntactically related words, annotated with syntactic relations.

Consider Figure~\ref{fig:comm}.
Imagine the speaker wants to communicate that Mary saw John.
The message (left) consists of a dependency structure with the words `saw', `Mary', `John', where Mary is the subject of the event denoted by `saw', and John is the object.
When uttering, the speaker needs to choose an ordering in which to order the words in this tree to generate a string of words.
In natural language, this order is largely determined by the \key{grammar} of the language:
The speaker will order it as (1) in English, and as (2) in Japanese.

@@

The listener receives a sentence -- a linear string of words -- and decodes the underlying message in accordance with the grammar of the language (right).
%Consistent with Shannon's model, we assume a Bayesian listener who decodes dependency structures probabilistically~(Figure~\ref{fig:comm}).
%If communication is successful, the listener can identify the intended structure with high confidence~(Figure~\ref{fig:comm}).

@@

The grammars of natural languages provide consistent ordering rules for all syntactic relations.
%All natural languages have some degree of word order regularities that are specified in their grammar.
%For instance, English places subjects before and objects after the verb, allowing the listener to unambiguously decode the sentence in Figure~\ref{fig:comm}.
%That is, speakers and listeners have shared knowledge of a \key{grammar} that specifies how dependency structures are encoded into sentences.
%Natural languages differ in the rules they apply: Some place the object after the verb, some place it before the verb.
%Speakers encode dependency trees into sentences according to a grammar~(Figure~\ref{fig:grammars}).
%While natural languages differ in the freedom of word order, all languages rely on some amount of word order reglarity to encode meaning.
This is illustrated in Figure~\ref{fig:grammars}:
We show how four different grammars order objects, adpositional phrases, and adpositions.
For instance, Grammar 1 -- corresponding to Arabic in Figure~\ref{fig:arabic-japanese-simple} -- orders objects (`friends', `letter') after verbs and has prepositions (`to friend').
Grammar 2 orders objects after verbs but has postpositions (`friend -- to').
Grammars 3 and 4 place the object before the verb, and one of them (Grammar 3) corresponds to Japanese order.

%\subsection{Efficiency in Word Order}
%Zipf

%We formalize Zipf's Forces of Unification and Diversification in

In Information Theory, the usefulness of a communication channel depends on (1) how costly encoding and transmission is, and (2) how precisely messages can be recovered from codes (REF).

@@

We formalize word order grammars as specifying how different types of dependents (subjects, objects, etc.) are ordered, employing a cross-linguistically meaningful inventory of relations~\cite{nivre2015universal}.
